---
title: "Exam 3"
output: html_notebook
---

Question : 

```{r}

quantile(Exam3_Q30$Data, type = 6)
median(Exam3_Q30$Data, type = 6)

quantile(Exam3_Q30$Data, type = 4)
median(Exam3_Q30$Data, type = 4)
```


 
```{r}

boxplot(Exam3_Q5, xlab="Wait Time in Minutes)", names =c("Wait"), horizontal = TRUE)

boxplot(Exam3_Q5, xlab="Wait Time (in Minutes)", names =c("Wait"), horizontal = TRUE, plot = FALSE, stats = FALSE)

EnvStats::summaryStats(Exam3_Q5$Data)
quantile(Exam3_Q5$Data, type = 6)


iqr(Exam3_Q5$Data)
30.5+(1.5*17)

```



```{r}

median(Exam3_Q6$Data)

stat(Exam3_Q6$Data)

```



Question 19

Weighted mean to recompute the averages of student grades by rows


```{r}
weighted.mean(Exam3_Q19$`Row Average Score`, Exam3_Q19$`Number of Students`)

mean(Exam3_Q19$`Row Average Score`)
```


Question 20


CHECK QUESTION 20

```{r}

```


Question 21

Standard Deviation

```{r}
summary(Exam3_Q21$Scores)

mean(Exam3_Q21$Scores)

geoMean(Exam3_Q21$Scores)

sd(Exam3_Q21$Scores)

```

Question 23

Covariance of GRE and GPA

```{r}
cov(Exam3_Q23$GRE, Exam3_Q23$GPA)

plot(Exam3_Q23, main = "Covariance of GRE and GPA", sub = "Covariance = 57.5")

lines(lowess(Exam3_Q23))
```

Question 27

Finding the mean of the values

```{r}
mean(Exam3_Q27$Data)

geoMean(Exam3_Q27$Data)

pop.geoMean(Exam3_Q27$Data)

```

Question 30 & 31 N=6



```{r}
sd(Exam3_Q30$Data)

pop.sd(Exam3_Q30$Data)

pop.var(Exam3_Q30$Data)
```





```{r}
pop.sd(Exam3_Q5$Data)
```

Question 32

Finding the 30th Percentile

```{r}
quantile(Exam3_Q32$Data, type = 6)

Quantile(Exam3_Q32$Data, type = 6)

quantile(Exam3_Q32$Data, probs = seq(0,1, by = 0.1), type = 6)
```

Question 33 & 34

IQR & 75th %tile

```{r}

IQR(Exam3_Q33$Data, type = 6)

quantile(Exam3_Q33$Data, type = 6)

```

Question 35 

median of frequency chart

```{r}
median(c(rep(5,15),rep(15,75),rep(25,55),(rep(35,55))))
```

Question 37 

Average score of a bowler based on sample (n=6)

```{r}
geoMean(Exam3_Q37$Scores)
```

Question 38 (use Exam3_Q33)

sd of sample study hours by 6 students

```{r}
sd(Exam3_Q33$Data)
"use top answer"
pop.sd(Exam3_Q33$Data)
```

Question 40

Mean Salary = 80,000 SD=6,000 what is SD with a 2% raise of all salaries

```{r}
median
```

Question 42 

Geometric mean is greater than the arithmetic mean?

```{r}
geoMean(Exam3_Q33$Data)

mean(Exam3_Q33$Data)

```

Question 43

Addidas average growthrate

```{r}

killpack.return.calc(Exam3_Q43$Growth)

```

Question #48 (same data as #5)

find IQR

```{r}
IQR(Exam3_Q5$Data, type = 6)
```

Question #50

Median over Philidelphia temperatures

```{r}
median(Exam3_Q50$Temperture)

median
```





```{r}
KillpackStatsPackage::killpack.return.calc(Exam3_Q43$Growth)
pop.sd(Exam3_Q50$Temperture)
pop.var(Exam3_Q50$Temperture)
```



```{r}
plot(mlb_elo$score1, mlb_elo$score2, xlab = "Home-Team Score", ylab = "Visiting-Team Score", main = "Score Analasys")

lines(lowess(mlb_elo$score1, mlb_elo$score2))

plot(mlb_elo$score1, mlb_elo$score2, type = "n")
```




```{r}
IQR(Exam3_Q33$Data, type = 6)
```






