---
title: "Chapter 5 Quiz"
output: html_notebook
---


```{r}
knitr::opts_chunk$set(echo = FALSE)
```


###Question 1

Assume that X is a Poisson random variable with μ = 28. Calculate the following probabilities.

P(X ≤ 18)

P(X = 20)

P(X > 22)

P(24 ≤ X ≤ 32)


```{r}
print("less than or equal to")
ppois(18, lambda = 28)
print("equal to the value")
dpois(20, lambda = 28)

print("everything thats greater than 22")
1-(dpois(22, lambda = 28))

print("P(24 ≤ X ≤ 32)")
(ppois(32, lambda = 28))-(ppois(24, lambda = 28))

```

###Question 2

You are considering two mutual funds as an investment. The possible returns for the funds are dependent on the state of the economy and are given in the accompanying table.

    State of the economy     fund 1   fund 2    likelyhood
    Good                      36%      20%         12%
    Fair                      11%      17%         43%
    Poor                      -9%     -17%         45%

a. Find the expected value and the standard deviation of returns for Fund 1. (Round intermediate calculations to at least 4 decimal places and final answers to 2 decimal places.)

b. Find the expected value and the standard deviation of returns for Fund 2. (Round intermediate calculations to at least 4 decimal places and final answers to 2 decimal places.)

c. Which fund will you pick if you are risk averse?

```{r}
print("A. Fund 1 Mean, VAR, SD")
#Fund 1
wm.a=w.mean(c(.36,.11,-.09),c(.12,.43,.45))
wsd.a=w.sd(c(.36,.11,-.09),c(.12,.43,.45))
wva.a=w.var(c(.36,.11,-.09),c(.12,.43,.45))


wm.a
wva.a
wsd.a

print("B. Fund 2 Mean, VAR, SD")
#Fund 2
wm.b=w.mean(c(.2,.17,-.17),c(.12,.43,.45))
wsd.b=w.sd(c(.2,.17,-.17),c(.12,.43,.45))
wva.b=w.var(c(.2,.17,-.17),c(.12,.43,.45))


wm.b
wva.b
wsd.b

print("C. Fund 1 bc/ higher expected return, less loss if its bad, and less deviation meaning its more consistant")

```


###Question 3

Suppose 53% of recent college graduates plan on pursuing a graduate degree. Twelve recent college graduates are randomly selected.

a. What is the probability that no more than three of the college graduates plan to pursue a graduate degree? (Do not round intermediate calculations. Round your final answers to 4 decimal places.)

b. What is the probability that exactly seven of the college graduates plan to pursue a graduate degree? (Do not round intermediate calculations. Round your final answers to 4 decimal places.)

c. What is the probability that at least six but no more than eleven of the college graduates plan to pursue a graduate degree? (Do not round intermediate calculations. Round your final answers to 4 decimal places.)


```{r}
#dbinom(x,n,p) (X = x)
#pbinom(x,n,p) (X ≤ x)

#A
pbinom(3,12,.54)

#B
dbinom(7,12,.54)

#C
pbinom(11,12,.54)-pbinom(5,12,.54)
```


###Question 4

An analyst has developed the following probability distribution for the rate of return for a common stock.

 
    Scenario    Probability     Rate of Return
       1          0.23             -10%
       2          0.42               3%
       3          0.35              16%
    
a. Calculate the expected rate of return. (Round intermediate calculations to at least 4 decimal places. Round your answer to 2 decimal places.)

```{r}
print("A: Expected Rate of Return")
#Fund
wm.c=w.mean(c(-.1,.03,.16),c(.23,.42,.35))

wm.c
```

b. Calculate the variance and the standard deviation of this probability distribution. (Use the percentage values for your calculations (for example 10% not 0.10). Round intermediate calculations to at least 4 decimal places. Enter your answer as a percentage rounded to 2 decimal places.)
```{r}
print("B: VAR & %, SD & %")
#Fund
wsd.c=w.sd(c(-.1,.03,.16),c(.23,.42,.35))
wva.c=w.var(c(-.1,.03,.16),c(.23,.42,.35))

wva.c
(wva.c)*100
wsd.c
(wsd.c)*100
```


###Question 5

India is the second most populous country in the world, with a population of over 1 billion people. Although the government has offered various incentives for population control, some argue that the birth rate, especially in rural India, is still too high to be sustainable. A demographer assumes the following probability distribution for the household size in India.

    Household Size      Probability
    1                   0.03
    2                   0.11
    3                   0.15
    4                   0.24
    5                   0.16
    6                   0.16
    7                   0.11
    8                   0.04

    
a. What is the probability that there are less than 5 members in a household in India? (Round your answer to 2 decimal places.)



```{r}
print("1   2    3    4    5    6    7    8    ")
cumsum(Quiz5Q5$frequency)
```


b. What is the probability that there are 5 or more members in a household in India? (Round your answer to 2 decimal places.)

```{r}
1-.53
```


c. What is the probability that the number of members in a household in India is strictly between 2 and 5? (Round your answer to 2 

```{r}
0.53-0.14
```

###Question 6

Consider the following discrete probability distribution.
   
    x        -40   -10   10   20
    P(X=x)   0.37  0.15      0.12
    
a. Complete the probability distribution. (Round your answer to 2 decimal places.) P(X=10)

```{r}
1-sum(c(0.37,0.15,0.12))
```

    x        -40   -10   10   20
    P(X=x)   0.37  0.15 0.36 0.12


b. What is the probability that the random variable X is positive? (Round your answer to 2 decimal places.)

```{r}
0.36+0.12
```


c. What is the probability that the random variable X is greater than −35? (Round your answer to 2 decimal places.)

```{r}
0.15+0.36+0.12
```


d. What is the probability that the random variable X is less than 20? (Round your answer to 2 decimal places.)

```{r}
1-0.12
```


###Question 6

Calculate the mean, the variance, and the standard deviation of the following discrete probability distribution. (Negative values should be indicated by a minus sign. Round intermediate calculations to at least 4 decimal places. Round your final answers to 2 decimal places.)


    x         -33      -26     -9      -5
    P(X=x)    0.47     0.29    0.19    0.05

```{r}
print("A. Fund 1 Mean, VAR, SD")
#Fund 1
wm.q6a=w.mean(c(-33, -26, -9, -5),c(0.47, 0.29, 0.19, 0.05))
wsd.q6a=w.sd(c(-33, -26, -9, -5),c(0.47, 0.29, 0.19, 0.05))
wva.q6a=w.var(c(-33, -26, -9, -5),c(0.47, 0.29, 0.19, 0.05))


wm.q6a
wva.q6a
wsd.q6a
```


































